A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-07 paper/paper.Rmd
Use proper title for figure legend

```{r Figure2, echo=FALSE, fig.cap="Season length and first appearance of powdery mildew in each respective trial for fifteen mungbean trials conducted in the Grains Research and Developmet (GRDC) Northern Grains Region of eastern Australia to evaluate the most effective time of fungicide application to save yield from powdery mildew infection. Trials were conducted from 2001 to 2019 by Queensland Department of Agriculture, Fisheries and Forestry, Northern Growers Alliance and University of Southern Queensland and coalated for meta-analysis."}
PM_Mdat %>%
  distinct(trial_ref, planting_date, harvest_date, first_sign_disease) %>%
  mutate(planting_date = ymd(planting_date)) %>%
  mutate(harvest_date = ymd(harvest_date)) %>%
  mutate(first_sign_disease = ymd(first_sign_disease)) %>%
  mutate(cropping_season = case_when(
    # add categorical value for estimated season period
    is.na(planting_date) | is.na(harvest_date) ~ "Estimated",
    TRUE ~ "Actual"
  )) %>%
  mutate(plant_day = case_when(
    #for crops planted in late December minus 365 days from yday function
    yday(planting_date) < 200 ~ yday(planting_date),
    yday(planting_date) > 200 ~ yday(planting_date) - 365,
  )) %>%
  mutate(season_length = case_when(
    # when either planting date or harvest date are missing use the overall mean season length as an estimate
    is.na(planting_date) | is.na(harvest_date) ~
      mean(yday(harvest_date) - plant_day, na.rm = TRUE),
    TRUE ~ yday(harvest_date) - plant_day
  )) %>%
  mutate(plant_day = case_when(
    # estimate planting day  from mean season length
    is.na(plant_day) ~ yday(harvest_date) - season_length,
    TRUE ~ plant_day
  )) %>%
  mutate(harvest_day = case_when(
    #estimate harvest day from mean season length
    is.na(harvest_date) ~ plant_day + season_length,
    TRUE ~ yday(harvest_date)
  )) %>%
  mutate(trial_ref = factor(trial_ref, # reorder by the first_sign_of_disease
                            levels = trial_ref[rev(order(ymd(first_sign_disease)))])) %>%
  ggplot() +
  geom_pointrange(
    aes(
      x = trial_ref,
      y = yday(first_sign_disease),
      ymin = plant_day,
      ymax = harvest_day,
      colour = cropping_season
    )
  ) +
  scale_y_continuous(
    limits = c(-25,
               183),
    labels = paste(month(1:7, label = TRUE, abbr = TRUE), rep(1, 7), sep = "-"),
    breaks = yday(ymd(paste(
      rep(2018, 7), 1:7, rep(1, 7), sep = "-"
    )))
  ) +
  geom_hline(yintercept = yday(ymd(paste(
    rep(2018, 7), 1:7, rep(1, 7), sep = "-"
  ))),
  colour = "grey80",
  linetype = 2) +
  geom_point(aes(x = trial_ref, y = yday(first_sign_disease))) +
  coord_flip() +
  scale_color_manual(values = c("black", "grey70")) +
  ggtitle("Season length and first appearance of powdery mildew\nin each respective trial") +
  xlab("Trial reference code") +
  ylab(NULL)
```

>>>>

```{r Figure2, echo=FALSE, fig.cap="Season length and first appearance of powdery mildew in each respective trial for fifteen mungbean trials conducted in the Grains Research and Developmet (GRDC) Northern Grains Region of eastern Australia to evaluate the most effective time of fungicide application to save yield from powdery mildew infection. Trials were conducted from 2001 to 2019 by Queensland Department of Agriculture, Fisheries and Forestry, Northern Growers Alliance and University of Southern Queensland and coalated for meta-analysis."}
PM_Mdat %>%
  distinct(trial_ref, planting_date, harvest_date, first_sign_disease) %>%
  mutate(planting_date = ymd(planting_date)) %>%
  mutate(harvest_date = ymd(harvest_date)) %>%
  mutate(first_sign_disease = ymd(first_sign_disease)) %>%
  mutate(cropping_season = case_when(
    # add categorical value for estimated season period
    is.na(planting_date) | is.na(harvest_date) ~ "Estimated",
    TRUE ~ "Actual"
  )) %>%
  mutate(plant_day = case_when(
    #for crops planted in late December minus 365 days from yday function
    yday(planting_date) < 200 ~ yday(planting_date),
    yday(planting_date) > 200 ~ yday(planting_date) - 365,
  )) %>%
  mutate(season_length = case_when(
    # when either planting date or harvest date are missing use the overall mean season length as an estimate
    is.na(planting_date) | is.na(harvest_date) ~
      mean(yday(harvest_date) - plant_day, na.rm = TRUE),
    TRUE ~ yday(harvest_date) - plant_day
  )) %>%
  mutate(plant_day = case_when(
    # estimate planting day  from mean season length
    is.na(plant_day) ~ yday(harvest_date) - season_length,
    TRUE ~ plant_day
  )) %>%
  mutate(harvest_day = case_when(
    #estimate harvest day from mean season length
    is.na(harvest_date) ~ plant_day + season_length,
    TRUE ~ yday(harvest_date)
  )) %>%
  mutate(trial_ref = factor(trial_ref, # reorder by the first_sign_of_disease
                            levels = trial_ref[rev(order(ymd(first_sign_disease)))])) %>%
  ggplot() +
  geom_pointrange(
    aes(
      x = trial_ref,
      y = yday(first_sign_disease),
      ymin = plant_day,
      ymax = harvest_day,
      colour = cropping_season
    )
  ) +
  scale_y_continuous(
    limits = c(-25,
               183),
    labels = paste(month(1:7, label = TRUE, abbr = TRUE), rep(1, 7), sep = "-"),
    breaks = yday(ymd(paste(
      rep(2018, 7), 1:7, rep(1, 7), sep = "-"
    )))
  ) +
  geom_hline(yintercept = yday(ymd(paste(
    rep(2018, 7), 1:7, rep(1, 7), sep = "-"
  ))),
  colour = "grey80",
  linetype = 2) +
  geom_point(aes(x = trial_ref, y = yday(first_sign_disease))) +
  coord_flip() +
  scale_color_manual(values = c("black", "grey70"), name = "Cropping Season") +
  xlab("Trial reference code") +
  ylab(NULL)
```
